\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-22 Data_csv/Paper/paper.tex
last and final and that's all

\begin{abstract}

In the case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant. However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities. Bioaugmentation is a method that could be used to help them overcome the effect of pollution. It is the addition of bacteria able to degrade the pollutant into the contaminated environment. In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20. Each component in equal concentration} substrate. As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
Our results are encouraging and would deserve some further experimentations. However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{Pseudomonas putida}.

@@

Toluene is an organic solvent widely used in the paint or cosmetic industry nowadays. It is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}. 
When such event happens, one way to treat it is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant to a native community, allowing it to grow back \cite{Bioremediation}.

@@

%ALTERNATIVE 1

%In our experiment we wanted to know if this ability to metabolize toluene could not only have a positive effect on a native community, for example by lowering the toluene concentration or by producing metabolites that the bacteria from SC could use as carbon source. Our hypothesis for this experiment was that the addition of \textit{Pseudomonas putida} or \textit{Pseudomonas veronii} will have an effect on SC growth, especially in a toluene-only media. 
%ALTERNATIVE 2

%Our hypothesis for this experiment was that the addition of Pseudomonas putida or Pseudomonas veronii will have an effect on SC growth, especially in a toluene-only media.
%Ideed, we think that these Pseudomonas bacteria could produce metabolites the SC bacteria could use as carbon source or reduce the toluene concentration and thus it's toxic effect. This would lead to a better growth of the sand community in presence of one of these pseudomonas strains.

@@

\subsection{Experimental design}
Apart from SC, we used two bacterial strains : \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry) and \textit{Pseudomonas putida F1}(also tagged with mCherry).

However, keep in mind that SC isn't a single species of bacteria, but rather a community containing potentially many different species.
%There were 3 bacterial cultures used for this experiment: \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry, called PV), \textit{Pseudomonas putida F1}(tagged with mCherry, called PP) and a Sand Community, extracted from the beach of St-Sulpice. 
We experimented with two media: a mixed carbon medium\textsuperscript{1} and a Minimal Media 1x (MM) with only toluene as carbon source.

We separated the work into two weeks, testing SC and PP during Week 1 and SC and PV during Week 2. In each experiment, we tested the 2 communities and their interaction in mixed carbon and toluene.

\begin{figure}[H]

		\includegraphics[width=9cm]{erlenmeyer.PNG}
		\caption{Experimental design. Experiments were separated into 2 weeks, with triplicates for each bacterial culture. The number of cells was measured at multiple timepoints.}
		\label{design_weeks}

As controls, we used SC alone in both media, to prove that the medium has an effect and compare with the interaction of species. PP(or PV) alone in both media are used to show that the medium has no effect.
We therefore had 6 unique treatments, and used 3 replicates for each. We ended up with 18 cultures per experiment. These cultures were then sampled and counted regularly with a flow cytometer at different timepoints. The timespan between two timepoints had to vary to fit our personal schedules.

@@

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{aucscw1} and \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue points).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow points).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc1.png}
	\caption{Week 1 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw1}
\end{figure}%
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpp1.png}
	\caption{Week 1 - PP : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucppw1}
\end{figure}
absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.

@@

\subsubsection{Total cell count comparison}
The total cell count over time is represented on Fig. \ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first week. It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.\newline

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_mixC2.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
	\label{totcountmixC2text}
\end{figure}
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_tol2.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcounttol2text}
\end{figure}
\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{aucscw2} and \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene (red curves/points). It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that SC behaved differently from one week to another and thus cannot be considered identical. Therefore, we won't be able to compare the results from the two weeks. 
The Anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline

\subsubsection{Pseudomonas veronii}
The growth of PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$). While not being as significant as our other results, it could indicate some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc2.png}
	\caption{Week 2 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw2}
\end{figure}%
\vspace{-0.3cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpv2.png}
	\caption{Week 2 - PV : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucpvw2}
\end{figure}

@@

To circumvent this problem, another tagging method unaffected by cell death could be used (Fig. \ref{antibody}). For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells. This would allow a better differentiation of our communities.

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
		\label{problemw1}
\end{figure}

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw2.PNG}
		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
		\label{problemw2}

%\caption{Fig. \ref{problemw1} : Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Fig. \ref{problemw2} : Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
%\label{problemsyto}

@@

\begin{figure}
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=4.3cm]{PP3T5.png}
		\caption{}
		\label{problemflow1}
	\end{subfigure}%
	\begin{subfigure}{.22\textwidth}
		\centering		
		\includegraphics[width=4.3cm]{PPSC1T5.png}
		\caption{}
		\label{problemflow2}				
	\end{subfigure}
	\caption{Scatterplot of a stained PP sample(Fig. \ref{problemflow1}) besides a stained PPSC sample (Fig. \ref{problemflow2}). They look very similar. A lot of PP seem to have lost mCherry (red) fluorescence and have shifted downwards (Fig. \ref{problemflow1}) and look like the supposed SC cells in Fig. \ref{problemflow2}.  }
	\label{problemflow}
\end{figure}

% Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig. \ref{scatter1} and \ref{scatter2}). Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig. \ref{problemw1}) or PVSC (Fig. \ref{problemw2}).
% 
%It is even more visible in Fig.\ref{problemflow}. Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene. These graphs are almost identical, and both show a green-only fluorescence.
% 
%
%Our hypothesis is that some PP/PV cells died, but weren’t lysed. Their DNA being still nicely protected they could be stained by SYTO-9. However, their metabolic activities stopped, reducing mCherry fluorescence. Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.

%\subsection{Improvements}

%Another point that could be interesting to change is the initial concentration of PP and PV. Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV. Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media. 
%
%In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
%The high quantity of a single strain may have made it easier for them  to outgrow SC over time.

%Finally, as often in the lab, our results seem to unveil more questions than answers. We would have liked, if time allowed it, to perform additional experiments proposed above. Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before. 
%
%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above. The issue with this staining technique might carry some artefacts that should be considered in data interpretation.

\subsection{Bacterial interactions}
To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
\begin{figure}[H]
	\centering

\end{figure}
If we assume this tagging issue is negligible, we can infer on the growth of each population separately within each treatment. In the first week, the data indicates that the presence of PP affects SC differently depending on the media (Interaction: F = 26.62, df = 1, $p = 8,64 \cdot 10^{-4}$).  In toluene, it allows a better growth but has no effect in the mix carbon media.  There is an important effect of the media in absence of PP: SC alone grows significantly less in toluene than in mixed carbon. Furthermore, PP shows an important difference in AUC between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$) and no difference due to the presence of SC.

>>>>

\begin{abstract}
In case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant. However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities. But bioaugmentation, the addition of a bacteria able to degrade a pollutant in order to remove that pollutant from the environment, might also have positive side effects on the growth of the original bacterial community. Furthermore, the survival of the added bacteria and thus the efficiency of bioaugmentation depends a lot on its capacity to grow in presence of the original bacterial community. In that context, we chose to study the interaction of a bacterial community extracted from sand and two toluene degrading bacteria: \textit{Pseudomonas putida} F1  or \textit{Pseudomonas veronii} YdBTEX2 (both tagged with fluorescent mCherry protein). To do so, we grew them in batch cultures either with toluene only or with mixed carbon\footnote{Mixed Carbon media composition : L-Arginine, D-Xylose, Aspartic acid potassium salt, 2-Hydroxybenzoic acid, L-Phenylalanine, L-Serine, Gamma Hydroxy butyric acid, D-cellobiose, alpha-D-Lactose, Putrescine, Itaconic acid, alpha-D-Glucose-1-phosphate, D-Glucosaminic acid, N-acetyl-D-glucosamine, 4-Hydroxy benzoic acid, D-Mannitol, meso-erytritol, Galacturonic acid, Methyl pyruvate, Tween 20. Each component in equal concentration} substrate. We used flow cytometry at different time points to measure the growth of each population separatly. If we consider negligible the difficulty we had to distingish the two populations (see \textit{Discussion}), our results notably indicate that the bacterial commnuity grows better in toluene in presence of \textit{Pseudomonas putida} F1 than alone.

%In the case of an environmental pollution, the microbial community of the soil will have an important role in the degradation of the pollutant. However, adaptation to the sudden change in the soil composition is difficult for most bacterial communities. Bioaugmentation is a method that could be used to help them overcome the effect of pollution. It is the addition of bacteria able to degrade the pollutant into the contaminated environment. In our experiment, we chose to add \textit{Pseudomonas veronii} 1YdBTEX2 and \textit{Pseudomonas putida F1} (both tagged with fluorescent mCherry protein) to a bacterial community extracted from sand and to grow them either with toluene only or with mixed carbon substrate. As the two \textit{Pseudomonas} strains we added are able to degrade toluene, we wanted to know if the addition of one of these strain to this bacterial community would have an effect on the growth of this community.
%Our results are encouraging and would deserve some further experimentations. However, unlike usual bioaugmentation experiments in literature, our results indicate that the Sand Community was almost entirely replaced by \textit{Pseudomonas veronii} or \textit{Pseudomonas putida}.

@@

Toluene is an organic solvent widely used in the paint or cosmetic industry nowadays. It is a monoaromatic volatile molecule which is toxic and ecotoxic \cite{toluene}. 
When such event happens, one way to treat it is the use of bioremediation. There are several different techniques of bioremediation but they all have the same purpose: to use live organisms to get rid of pollutants. The technique that interested us in this experiment was bioaugmentation, the addition of a microorganism able to degrade the targeted pollutant in order to remove that pollutant from the environment \cite{Bioremediation}. We wanted to know if that also had a potentially positive side effects on the original bacterial community's growth.

@@

@@

\subsection{Experimental design}
Apart from SC, we used two bacterial strains : \textit{Pseudomonas veronii} 1YdBTEX2 (tagged with mCherry) and \textit{Pseudomonas putida F1}(also tagged with mCherry).However, keep in mind that SC isn't a single species of bacteria, but rather a community containing potentially many different species.
We experimented with two media: a mixed carbon medium\textsuperscript{1} and a Minimal Media 1x (MM) with only toluene as carbon source. We separated the work into two weeks, testing SC and PP during Week 1 and SC and PV during Week 2. In each experiment, we tested the 2 communities and their interaction in mixed carbon and toluene (see Fig. \ref{design_weeks}). As controls, we used SC alone in both media, to prove that the medium has an effect and compare with the interaction of species. PP(or PV) alone in both media are used to show that the medium has no effect.
\begin{figure}[H]
	\includegraphics[width=9cm]{erlenmeyer.PNG}
	\caption{Experimental design. Experiments were separated into 2 weeks, with triplicates for each bacterial culture. The number of cells was measured at multiple timepoints.}
	\label{design_weeks}

\end{figure}
We therefore had 6 unique treatments, and used 3 replicates for each. We ended up with 18 cultures per experiment. These cultures were then sampled and counted regularly with a flow cytometer at different timepoints. The timespan between two timepoints had to vary to fit our personal schedules.

@@

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{aucscw1} and \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue points).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow points).

We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a  better growth but has no effect in the mix carbon media. 
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc1.png}
	\caption{Week 1 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw1}
\end{figure}%
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpp1.png}
	\caption{Week 1 - PP : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucppw1}
\end{figure}In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.

@@

\subsubsection{Total cell count comparison}
The total cell count over time is represented on Fig. \ref{totcountmixC2text} and \ref{totcounttol2text}, the conclusion is the same as in the first week. It shows no signs that growing PV and SC together influences the growth of the overall population nor the total cell count after 48 hours, in a mixed carbon or toluene media.

\begin{figure}
	\centering
	\includegraphics[width=9cm]{totcount_mixC2.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
	\label{totcountmixC2text}
\end{figure}

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{aucscw2} and \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene (red curves/points). It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that SC behaved differently from one week to another and thus cannot be considered identical. Therefore, we won't be able to compare the results from the two weeks.

The Anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.

\subsubsection{Pseudomonas veronii}
The growth of PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold better in toluene (red and orange) than in mixed carbon (black and blue curves/points).

One can also notice that PP grew slightly less in presence of SC, \begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_tol2.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcounttol2text}
\end{figure}
\vspace{-0.5cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc2.png}
	\caption{Week 2 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw2}
\end{figure}%
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpv2.png}
	\caption{Week 2 - PV : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucpvw2}
\end{figure}in both media (blue and yellow compared to black and red curves/points). 
The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$). 
While not being as significant as our other results, it could indicate some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

@@

To circumvent this problem, another tagging method unaffected by cell death could be used (Fig. \ref{antibody}). For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells. This would allow a better differentiation of our communities.
\begin{figure}[H]
	\centering

@@

\subsection{Bacterial interactions}
To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{problemw1.PNG}
	\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
	\label{problemw1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{problemw2.PNG}
	\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
	\label{problemw2}
\end{figure}

\begin{figure}[H]
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=4.3cm]{PP3T5.png}
		\caption{}
		\label{problemflow1}
	\end{subfigure}%
	\begin{subfigure}{.22\textwidth}
		\centering		
		\includegraphics[width=4.3cm]{PPSC1T5.png}
		\caption{}
		\label{problemflow2}				
	\end{subfigure}
	\caption{Scatterplot of a stained PP sample(Fig. \ref{problemflow1}) besides a stained PPSC sample (Fig. \ref{problemflow2}). They look very similar. A lot of PP seem to have lost mCherry (red) fluorescence and have shifted downwards (Fig. \ref{problemflow1}) and look like the supposed SC cells in Fig. \ref{problemflow2}.  }
	\label{problemflow}
\end{figure} 
If we assume this tagging issue is negligible, we can infer on the growth of each population separately within each treatment. In the first week, the data indicates that the presence of PP affects SC differently depending on the media (Interaction: F = 26.62, df = 1, $p = 8,64 \cdot 10^{-4}$).  In toluene, it allows a better growth but has no effect in the mix carbon media.  There is an important effect of the media in absence of PP: SC alone grows significantly less in toluene than in mixed carbon. Furthermore, PP shows an important difference in AUC between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$) and no difference due to the presence of SC.
